paper

### 2023-02-16 outputs/paper/paper.qmd
Testing reading in data

```{r}
#install.packages('haven')
library(haven)
raw_data <- read_dta("inputs/data/survey.dta")
```

>>>>

```{r}
#install.packages('haven')
#install.packages('here')

library(here)
library(haven)

raw_data <- read_dta(here::here("inputs/data/survey.dta"))

dat_male <- dat_use[dat_use$gender == "Male"

raw_data$gender

raw_data <- raw_data[raw_data$gender == "Male"]
```
